---
title: "Love vs extraterrestials"
author: "Evangela Mcgarity"
date: "Spring 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
help("m111surveyfa13")
mydata<-m111surveyfa13 <- na.omit(m111surveyfa13)
```

# A question of Belief

Your data is in the dataframe called "mydata" examine it in the environment tab  
do a variable analysis on the 3 Questions and then upload the appropriate Rmd template for this job.   
Also create an empty github repository called "Belief" and make it the remote repository for  
this assignment.  For each question supply graphical evidence, numerical summaries, an inferential test, and a conclusion.  When finished push your rmd file, your project file, and your knitted html file to your github repo.  Finally turn in to Canvas the link to your github repo.



# Your First Question  

### Do people who believe in Love at First sight also tend to believe in Life on other planets?

$H_0$: There is no belief in love at first site and belief in et.
$A_A$: there is belief in love at first site and in et.

graphic display

```{r}
barchartGC(~love_first + extra_life,data=mydata, xlab="love at first site")
```
people who believe in first site also tend to beleive in et

numerical summary 

```{r}
table1 <- xtabs(~love_first + extra_life, data=mydata)
rowPerc(table1)
colPerc(table1)
```  
it looks about the same 

inference


```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

We fail to reject it,there has no evidence to support the contention because the p value is higher then p<0.05

# Your second Question 


### Is there a difference between boys and girls with respect to belief in life on other planets?
$H_0$: There is no relation between boys and girls belief in life on other planets.
$A_A$: there is belief in life on ither planets between boys and girls.





graphical summary
```{r}
barchartGC(~sex + extra_life,data=mydata)
```
  Boys seems to believe in life on other planet more than girls
  
  numerical summary
  
```{r}
table1 <- xtabs(~sex + extra_life, data=mydata)
rowPerc(table1)
colPerc(table1)
```  
 
 Inference
 
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
 we fail to reject the hypotheseis because the p value is higher then 0.05
 
# Your last Question  

### Is there a difference between boys and girls with respect to belief in love at First sight?
$H_0$: there is no relation between boys and girls with respect to love at first site.
$A_A$: there is a relation between boys and girls with respect to love at first site.




graphical summary
```{r}
barchartGC(~sex + love_first,data=mydata)
```
Boys do not believe in Love at first site.
 numerical summary
  
```{r}
table1 <- xtabs(~sex + extra_life, data=mydata)
rowPerc(table1)
colPerc(table1)
```  
Boys do not believe in love at first site.
Inference
 
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
We fail to reject it because it is higher then p value 0.05